---
title: "04_5_construct_figuretable_test_linear_linear_optimal_iv"
author: "Suguru Otani"
date: "2022/12/03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load

```{r,echo=FALSE,results = 'asis'}
rm(list = ls())
library(magrittr)
library(ggplot2)
# set constant ----
n_observation_list <-
  c(
    50,
    100,
    200, 
    1000,
    2000,
    5000,
    10000
  )
sigma_list <-
  c(
    #0.001,
    #0.5, 
    1.0#, 
    #2.0
  )
alpha2_list <-
  c(
    0.1,
    0.5,
    1.0,
    5.0,
    20.0
  )
theta_list <-
  c(
    0.05,
    0.1,
    0.2,
    0.33,
    0.5,
    1.0
  )
for(nn in 1:length(n_observation_list)){
  for(ss in 1:length(sigma_list)){
    for(aa in 1:length(alpha2_list)){
      for(tt in 1:length(theta_list)){
        temp_nn <-
          n_observation_list[nn]
        temp_sigma <-
          sigma_list[ss]
        temp_theta <-
          theta_list[tt]
        temp_alpha2 <-
          alpha2_list[aa]
        filename <-
          paste(
            "linear_linear_",
            "n_",
            temp_nn,
            "_theta_",
            temp_theta,
            "_alpha2_",
            temp_alpha2,
            "_sigma_",
            temp_sigma,
            sep = ""
          )
        #cat(filename,"\n")
        temp_data <-
          readr::read_csv(
            file =
              here::here(
                paste(
                  "output/testing_project/",
                  "parameter_hat_table_",
                  filename,
                  "_linear_optimal_separate",
                  ".csv",
                  sep = ""
                  )
                ),
            show_col_types = FALSE
            )
        assign(
          filename,
          temp_data
          )
        reject_probability <-
          sum((temp_theta/(temp_data$sd_θ/sqrt(temp_nn))) > 1.96)/100
        if(nn == 1 & ss == 1 & aa == 1 &tt == 1){
          data_for_plot_iv_optimal <-
            cbind(
              temp_nn,
              temp_theta,
              temp_alpha2,
              temp_sigma,
              reject_probability
              ) %>% 
            tibble::as_tibble() 
        }else{
          data_for_plot_temp <-
            cbind(
              temp_nn,
              temp_theta,
              temp_alpha2,
              temp_sigma,
              reject_probability
              ) %>% 
            tibble::as_tibble() 
          data_for_plot_iv_optimal <-
            rbind(
              data_for_plot_iv_optimal,
              data_for_plot_temp
              )
        }
      }
    }
  }
}
# benchmark
for(nn in 1:length(n_observation_list)){
  for(ss in 1:length(sigma_list)){
    for(aa in 1:length(alpha2_list)){
      for(tt in 1:length(theta_list)){
        temp_nn <-
          n_observation_list[nn]
        temp_sigma <-
          sigma_list[ss]
        temp_theta <-
          theta_list[tt]
        temp_alpha2 <-
          alpha2_list[aa]
        filename <-
          paste(
            "data_linear_linear_",
            "n_",
            temp_nn,
            "_theta_",
            temp_theta,
            "_alpha2_",
            temp_alpha2,
            "_sigma_",
            temp_sigma,
            sep = ""
          )
        #cat(filename,"\n")
        temp_data <-
          readRDS(
            file =
              here::here(
                paste(
                  "output/testing_project/",
                  "parameter_hat_table",
                  filename,
                  ".rds",
                  sep = ""
                  )
                )
            )
        assign(
          filename,
          temp_data
          )
        reject_probability <-
          sum(temp_data$theta_hat_t_stats > 1.96)/100
        if(nn == 1 & ss == 1 & aa == 1 &tt == 1){
          data_for_plot <-
            cbind(
              temp_nn,
              temp_theta,
              temp_alpha2,
              temp_sigma,
              reject_probability
              ) %>% 
            tibble::as_tibble() 
        }else{
          data_for_plot_temp <-
            cbind(
              temp_nn,
              temp_theta,
              temp_alpha2,
              temp_sigma,
              reject_probability
              ) %>% 
            tibble::as_tibble() 
          data_for_plot <-
            rbind(
              data_for_plot,
              data_for_plot_temp
              )
        }
      }
    }
  }
}
data_for_plot_relative_rejection_probability <-
  data_for_plot_iv_optimal
data_for_plot_relative_rejection_probability$reject_probability_relative_to_benchmark <-
  (data_for_plot_iv_optimal$reject_probability + 0.01)/
  (data_for_plot$reject_probability + 0.01) # to avoid Inf

# colnames(data_for_plot) <-
#   c(
#     "M",
#     "$\\theta$",
#     "$\\alpha_2$",
#     "$\\sigma$",
#     "t-statistics"
#   )

options(modelsummary_format_numeric_latex = "plain") # for modelsummary output
```


# Estimation {.tabset}

## linear-demand linear-cost, $\sigma = 1$ {.tabset}

### $\theta = 0.05$ {.tabset}

#### $\alpha_2 = 0.1$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.05_alpha2_0.1_sigma_1)

```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.05_alpha2_0.1_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.05_alpha2_0.1_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.05_alpha2_0.1_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.05_alpha2_0.1_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.05_alpha2_0.1_sigma_1)
```


#### $\alpha_2 = 0.5$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.05_alpha2_0.5_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.05_alpha2_0.5_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.05_alpha2_0.5_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.05_alpha2_0.5_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.05_alpha2_0.5_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.05_alpha2_0.5_sigma_1)
```

#### $\alpha_2 = 1.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.05_alpha2_1_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.05_alpha2_1_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.05_alpha2_1_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.05_alpha2_1_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.05_alpha2_1_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.05_alpha2_1_sigma_1)
```


#### $\alpha_2 = 5.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.05_alpha2_5_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.05_alpha2_5_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.05_alpha2_5_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.05_alpha2_5_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.05_alpha2_5_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.05_alpha2_5_sigma_1)
```

#### $\alpha_2 = 20.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.05_alpha2_20_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.05_alpha2_20_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.05_alpha2_20_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.05_alpha2_20_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.05_alpha2_20_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.05_alpha2_20_sigma_1)
```


### $\theta = 0.1$ {.tabset}

#### $\alpha_2 = 0.1$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.1_alpha2_0.1_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.1_alpha2_0.1_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.1_alpha2_0.1_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.1_alpha2_0.1_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.1_alpha2_0.1_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.1_alpha2_0.1_sigma_1)
```


#### $\alpha_2 = 0.5$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.1_alpha2_0.5_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.1_alpha2_0.5_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.1_alpha2_0.5_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.1_alpha2_0.5_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.1_alpha2_0.5_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.1_alpha2_0.5_sigma_1)
```

#### $\alpha_2 = 1.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.1_alpha2_1_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.1_alpha2_1_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.1_alpha2_1_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.1_alpha2_1_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.1_alpha2_1_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.1_alpha2_1_sigma_1)
```


#### $\alpha_2 = 5.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.1_alpha2_5_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.1_alpha2_5_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.1_alpha2_5_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.1_alpha2_5_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.1_alpha2_5_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.1_alpha2_5_sigma_1)
```

#### $\alpha_2 = 20.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.1_alpha2_20_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.1_alpha2_20_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.1_alpha2_20_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.1_alpha2_20_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.1_alpha2_20_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.1_alpha2_20_sigma_1)
```

### $\theta = 0.2$ {.tabset}

#### $\alpha_2 = 0.1$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.2_alpha2_0.1_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.2_alpha2_0.1_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.2_alpha2_0.1_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.2_alpha2_0.1_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.2_alpha2_0.1_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.2_alpha2_0.1_sigma_1)
```

#### $\alpha_2 = 0.5$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.2_alpha2_0.5_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.2_alpha2_0.5_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.2_alpha2_0.5_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.2_alpha2_0.5_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.2_alpha2_0.5_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.2_alpha2_0.5_sigma_1)
```

#### $\alpha_2 = 1.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.2_alpha2_1_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.2_alpha2_1_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.2_alpha2_1_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.2_alpha2_1_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.2_alpha2_1_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.2_alpha2_1_sigma_1)
```


#### $\alpha_2 = 5.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.2_alpha2_5_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.2_alpha2_5_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.2_alpha2_5_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.2_alpha2_5_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.2_alpha2_5_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.2_alpha2_5_sigma_1)
```

#### $\alpha_2 = 20.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.2_alpha2_20_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.2_alpha2_20_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.2_alpha2_20_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.2_alpha2_20_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.2_alpha2_20_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.2_alpha2_20_sigma_1)
```


### $\theta = 0.33$ {.tabset}

#### $\alpha_2 = 0.1$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.33_alpha2_0.1_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.33_alpha2_0.1_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.33_alpha2_0.1_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.33_alpha2_0.1_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.33_alpha2_0.1_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.33_alpha2_0.1_sigma_1)
```

#### $\alpha_2 = 0.5$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.33_alpha2_0.5_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.33_alpha2_0.5_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.33_alpha2_0.5_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.33_alpha2_0.5_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.33_alpha2_0.5_sigma_1)
```


##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.33_alpha2_0.5_sigma_1)
```

#### $\alpha_2 = 1.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.33_alpha2_1_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.33_alpha2_1_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.33_alpha2_1_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.33_alpha2_1_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.33_alpha2_1_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.33_alpha2_1_sigma_1)
```


#### $\alpha_2 = 5.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.33_alpha2_5_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.33_alpha2_5_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.33_alpha2_5_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.33_alpha2_5_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.33_alpha2_5_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.33_alpha2_5_sigma_1)
```

#### $\alpha_2 = 20.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.33_alpha2_20_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.33_alpha2_20_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.33_alpha2_20_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.33_alpha2_20_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.33_alpha2_20_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.33_alpha2_20_sigma_1)
```


### $\theta = 0.5$ {.tabset}

#### $\alpha_2 = 0.1$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.5_alpha2_0.1_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.5_alpha2_0.1_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.5_alpha2_0.1_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.5_alpha2_0.1_sigma_1)
```


##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.5_alpha2_0.1_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.5_alpha2_0.1_sigma_1)
```

#### $\alpha_2 = 0.5$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.5_alpha2_0.5_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.5_alpha2_0.5_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.5_alpha2_0.5_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.5_alpha2_0.5_sigma_1)
```


##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.5_alpha2_0.5_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.5_alpha2_0.5_sigma_1)
```


#### $\alpha_2 = 1.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.5_alpha2_1_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.5_alpha2_1_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.5_alpha2_1_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.5_alpha2_1_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.5_alpha2_1_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.5_alpha2_1_sigma_1)
```

#### $\alpha_2 = 5.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.5_alpha2_5_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.5_alpha2_5_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.5_alpha2_5_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.5_alpha2_5_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_2000_theta_0.5_alpha2_5_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.5_alpha2_5_sigma_1)
```


#### $\alpha_2 = 20.0$ {.tabset}

##### $n = 50$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_50_theta_0.5_alpha2_20_sigma_1)
```

##### $n = 100$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_100_theta_0.5_alpha2_20_sigma_1)
```

##### $n = 200$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_200_theta_0.5_alpha2_20_sigma_1)
```

##### $n = 1000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.5_alpha2_20_sigma_1)
```

##### $n = 2000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_1000_theta_0.5_alpha2_20_sigma_1)
```

##### $n = 5000$

```{r,echo=FALSE,results = 'asis'}
modelsummary::datasummary_skim(
  fmt = 3,
  linear_linear_n_5000_theta_0.5_alpha2_20_sigma_1)
```


## Plot {.tabset}


### iv_optimal

```{r,echo=FALSE,results = 'asis'}
for(nn in 1:length(n_observation_list)){
  target_nn <-
    n_observation_list[nn]
  cat(target_nn,"\n")
  x <-
  ggplot(
  data_for_plot_iv_optimal %>%
    dplyr::filter(
      temp_nn == target_nn
    ),
  aes(
    x = as.character(temp_theta),
    y = reject_probability,
    fill =
      as.factor(
        temp_alpha2
        )
    )
  ) +
  geom_col(
    width = 0.2,
    position = position_dodge(0.7)
    ) +
  geom_hline(
    yintercept = 1.00,
    linetype = "dashed"
      ) +
  geom_hline(
  yintercept = 0.80,
  linetype = "dashed"
      ) +
  ylim(0, 1) +
  xlab(expression(theta == 1/N)) +
  ylab(paste("Rejection frequency",
             #target_nn,
             sep="")) +
  guides(fill = guide_legend(title = expression(alpha[2]))) +
  theme_classic() +
  theme(legend.position = 'top') +
  scale_fill_viridis_d()
  x
  # save
  figure_name <-
    paste(
      "../figuretable/theta_hat_power_separate_",
      target_nn,
      ".png",
      sep = ""
    )
  ggsave(filename = figure_name,
       plot = x,
       device = "png",
       width = 4,
       height = 3)

}

```

### iv_optimal relative to benchmark

```{r,echo=FALSE,results = 'asis'}
for(nn in 1:length(n_observation_list)){
  target_nn <-
    n_observation_list[nn]
  cat(target_nn,"\n")
  x <-
  ggplot(
  data_for_plot_relative_rejection_probability %>%
    dplyr::filter(
      temp_nn == target_nn
    ),
  aes(
    x = as.character(temp_theta),
    y = reject_probability_relative_to_benchmark,
    fill =
      as.factor(
        temp_alpha2
        )
    )
  ) +
  geom_col(
    width = 0.2,
    position = position_dodge(0.7)
    ) +
  geom_hline(
    yintercept = 1.00,
    linetype = "dashed"
      ) +
  # geom_hline(
  # yintercept = 0.80,
  # linetype = "dashed"
  #     ) +
  ylim(0, 101.1) +
  xlab(expression(theta == 1/N)) +
  ylab(paste("Rate of rejection frequency (optimal/base)",
             #target_nn,
             sep="")) +
  guides(fill = guide_legend(title = expression(alpha[2]))) +
  theme_classic() +
  theme(legend.position = 'top') +
  scale_fill_viridis_d()
  x
  # save
  figure_name <-
    paste(
      "../figuretable/theta_hat_power_iv_optimal_separate_relative_to_benchmark_",
      target_nn,
      ".png",
      sep = ""
    )
  ggsave(filename = figure_name,
       plot = x,
       device = "png",
       width = 4,
       height = 3)

}


```
