---
title: "10_1_simulate_counterexample_for_Lau1982_"
author: "Suguru Otani"
date: "2022/12/03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load

```{r,echo=FALSE,results = "asis"}
rm(list = ls())
library(magrittr)
library(ggplot2)
library(modelsummary) # for N in datasummary
# set constant ----
# set constant ----
n_observation_list <-
  c(
    50,
    100,
    200,
    1000
    )
sigma_list <-
  c(
    0.001,
    0.5,
    1.0,
    2.0
    )

# load, estimate, and save data ----
## linear demand and linear cost ----
### with demand_shifter_y ----
for(nn in 1:length(n_observation_list)){
  for(ss in 1:length(sigma_list)){
    temp_nn <-
      n_observation_list[nn]
    temp_sigma <-
      sigma_list[ss]
    filename <-
      paste(
        "linear_linear_",
        "n_",
        temp_nn,
        "_sigma_",
        temp_sigma,
        sep = ""
      )
    cat(filename,"\n")
    # load 
    target_data <-
      readRDS(
        file =
          here::here(
            paste(
              "output/data_",
              filename,
              ".rds",
              sep = ""
              )
            )
        )
    assign(
      filename,
      target_data)
  }
}
n_observation_list <-
  c(
    50,
    100,
    200,
    1000,
    1500
    )
# loglinear loglinear 
for(nn in 1:length(n_observation_list)){
  for(ss in 1:length(sigma_list)){
    temp_nn <-
      n_observation_list[nn]
    temp_sigma <-
      sigma_list[ss]
    filename <-
      paste(
        "loglinear_loglinear_",
        "n_",
        temp_nn,
        "_sigma_",
        temp_sigma,
        sep = ""
      )
    cat(filename,"\n")
    # load 
    target_data <-
      readRDS(
        file = 
          here::here(
            paste(
              "output/data_",
              filename,
              ".rds",
              sep = ""
              )
            )
        )
    assign(
      filename,
      target_data)
  }
}

generate_plot <-
  function(
    data
  ){
    temp <-
      data %>% 
      dplyr::filter(
        group_id_k < 10)
    x <-
      ggplot(temp,
             aes(x = Q, y = P)) + 
      geom_point(alpha = 0.3) + 
      stat_smooth(method = "lm",
                    se = FALSE) +
      theme_classic() + 
      scale_color_viridis_d() +
      theme(legend.position = 'top',
            legend.text = element_text(size=8)) +
      theme(plot.title = element_text(hjust = 0.5)) +
      xlab("Q") + 
      ylab("P")
    return(x)
  }

generate_plot_log_log <-
  function(
    data
  ){
    temp <-
      data %>% 
      dplyr::filter(
        group_id_k < 10)
    x <-
      ggplot(temp,
             aes(x = logQ, y = logP)) + 
      geom_point(alpha = 0.3) + 
      stat_smooth(method = "lm",
                    se = FALSE) +
      theme_classic() + 
      scale_color_viridis_d() +
      theme(legend.position = 'top',
            legend.text = element_text(size=8)) +
      theme(plot.title = element_text(hjust = 0.5)) +
      xlab("logQ") + 
      ylab("logP")
    return(x)
  }

options(modelsummary_format_numeric_latex = "plain") # for modelsummary output
```


# Estimation {.tabset}

## linear-demand linear-cost {.tabset}

\begin{align}
    P_t = \alpha_0 - (\alpha_1 + \alpha_2Z^R_t)Q_t + \alpha_3 Y_t + \varepsilon_{dt},\\
    MC_t = \gamma_0  + \gamma_1 Q + \gamma_2 w_t + \gamma_3 r_t + \varepsilon_{ct},
\end{align}
where $w_t$ and $r_t$ are excluded cost shifter.
The supply equation is given as
\begin{align}
    P_t = \gamma_0 + [\theta(\alpha_1 + \alpha_2Z^R_t)+ \gamma_1] Q_t   + \gamma_2 w_t + \gamma_3 r_t + \varepsilon_{ct}
\end{align}

From the supply equation and the demand equation, we can represent the aggregate quantity $Q_t$ based on the parameters and the exogenous variables as   
\begin{align}
    Q_t =  \frac{\alpha_0 + \alpha_3 Y_t - \gamma_0 - \gamma_2 w_t - \gamma_3 r_t + \varepsilon_{dt} - \varepsilon_{ct}}{(1 + \theta) (\alpha_1 + \alpha_2Z^R_t) + \gamma_1}.
\end{align}

### n = 50 {.tabset}

```{r,echo=TRUE,results = "asis"}
generate_plot(
    linear_linear_n_50_sigma_0.001
  )
generate_plot(
    linear_linear_n_50_sigma_0.5
  )
generate_plot(
    linear_linear_n_50_sigma_1
  )
generate_plot(
    linear_linear_n_50_sigma_2
  )
```


### n = 100

```{r,echo=TRUE,results = "asis"}
generate_plot(
    linear_linear_n_100_sigma_0.001
  )
generate_plot(
    linear_linear_n_100_sigma_0.5
  )
generate_plot(
    linear_linear_n_100_sigma_1
  )
generate_plot(
    linear_linear_n_100_sigma_2
  )
```


### n = 200 {.tabset}

```{r,echo=TRUE,results = "asis"}
generate_plot(
    linear_linear_n_200_sigma_0.001
  )
generate_plot(
    linear_linear_n_200_sigma_0.5
  )
generate_plot(
    linear_linear_n_200_sigma_1
  )
generate_plot(
    linear_linear_n_200_sigma_2
  )
```


### n = 1000 {.tabset}

```{r,echo=TRUE,results = "asis"}
generate_plot(
    linear_linear_n_1000_sigma_0.001
  )
generate_plot(
    linear_linear_n_1000_sigma_0.5
  )
generate_plot(
    linear_linear_n_1000_sigma_1
  )
generate_plot(
    linear_linear_n_1000_sigma_2
  )
```


## log-linear-demand log-linear-cost {.tabset}

Considers a model with log demand and a Cobb-Douglas cost function. 
The demand equation is given as a log-demand, 
\begin{align}
    \log P_{t} = \alpha_0 - (\alpha_1 + \alpha_2 Z^R_t) \log Q_t + \alpha_3 \log Y_t + \varepsilon_{dt}.
\end{align}
The log marginal cost is given as 
\footnote{\cite{hyde1995can} consider a Cobb-Douglas cost function such that \begin{align*}
    C_t = A^{-1/\gamma} \gamma \left(\frac{w_t}{\alpha}\right)^{\frac{\alpha}{\gamma}} \left(\frac{r_t}{\beta}\right)^{\frac{\beta}{\gamma}} Q_t^{\frac{1}{\gamma}}e^{\varepsilon_{ct}},
\end{align*} where $\alpha + \beta = \gamma$, and derive the log marginal cost function.}
\begin{align}
    \log MC_t &= \gamma_0 + \gamma_1 \log Q_t +  \gamma_2 \log w_t + \gamma_3 \log r_t + \varepsilon_{ct}.
\end{align}
Since $P'(Q) = - (\alpha_1 + \alpha_2 Z^R) \frac{P}{Q} $, the supply equation is given as
\begin{align}
    P_t &= \theta_t (\alpha_1 + \alpha_2 Z^R_t) \frac{P_t}{Q_t} Q_t + mc_t,
\end{align}
and by taking logarithm, we obtain
\begin{align}
    \log P_t & = - \log(1 - \theta(\alpha_1 + \alpha_2 Z^R_t)) + \gamma_0 + \gamma_1 \log Q_t +  \gamma_2 \log w_t + \gamma_3 \log r_t + \varepsilon_{ct}
\end{align}
From the supply equation and the demand equation, the log aggregate quantity is given as 
\begin{align}
    \log Q_t &= \frac{ \alpha_0 + \alpha_3 \log Y_t + \log (1 - \theta (\alpha_1 + \alpha_2 Z^R_t)) - \gamma_0  -  \gamma_2 \log w_t - \gamma_3 \log r_t + \varepsilon_{dt} - \varepsilon_{ct}}{\gamma_1+ \alpha_1 + \alpha_2 Z^R_t }.
\end{align}


\begin{align}
    &\log P_{t} = \alpha_0 - \alpha_1 \log Q_t - \alpha_2 Z^R_t\log Q_t + \alpha_3 \log Y_t \varepsilon_{dt},\\
    &\log P_t  = - \log(1 - \theta(\alpha_1 + \alpha_2 Z^R_t)) + \gamma_0 + \gamma_1 \log Q_t +  \gamma_2 \log w_t + \gamma_3 \log r_t + \varepsilon_{ct}.
\end{align}

### n = 50 {.tabset}

```{r,echo=TRUE,results = "asis"}
generate_plot_log_log(
    loglinear_loglinear_n_50_sigma_0.001
  )
generate_plot_log_log(
    loglinear_loglinear_n_50_sigma_0.5
  )
generate_plot_log_log(
    loglinear_loglinear_n_50_sigma_1
  )
generate_plot_log_log(
    loglinear_loglinear_n_50_sigma_2
  )
```


### n = 100

```{r,echo=TRUE,results = "asis"}
generate_plot_log_log(
    loglinear_loglinear_n_100_sigma_0.001
  )
generate_plot_log_log(
    loglinear_loglinear_n_100_sigma_0.5
  )
generate_plot_log_log(
    loglinear_loglinear_n_100_sigma_1
  )
generate_plot_log_log(
    loglinear_loglinear_n_100_sigma_2
  )
```


### n = 200 {.tabset}

```{r,echo=TRUE,results = "asis"}
generate_plot_log_log(
    loglinear_loglinear_n_200_sigma_0.001
  )
generate_plot_log_log(
    loglinear_loglinear_n_200_sigma_0.5
  )
generate_plot_log_log(
    loglinear_loglinear_n_200_sigma_1
  )
generate_plot_log_log(
    loglinear_loglinear_n_200_sigma_2
  )
```


### n = 1000 {.tabset}

```{r,echo=TRUE,results = "asis"}
generate_plot_log_log(
    loglinear_loglinear_n_1000_sigma_0.001
  )
generate_plot_log_log(
    loglinear_loglinear_n_1000_sigma_0.5
  )
generate_plot_log_log(
    loglinear_loglinear_n_1000_sigma_1
  )
generate_plot_log_log(
    loglinear_loglinear_n_1000_sigma_2
  )
```


### n = 1500 {.tabset}

```{r,echo=TRUE,results = "asis"}
generate_plot_log_log(
    loglinear_loglinear_n_1500_sigma_0.001
  )
generate_plot_log_log(
    loglinear_loglinear_n_1500_sigma_0.5
  )
generate_plot_log_log(
    loglinear_loglinear_n_1500_sigma_1
  )
generate_plot_log_log(
    loglinear_loglinear_n_1500_sigma_2
  )